Efficient, Robust and Exact Boolean Operations on N Triangular Mesh Primitives

### 2016-11-21 summary.tex
cao

As the precision of input coordinates is finite, we can determine in advance the upper boundary of precision needed to perform a precise decision, with which we can use fixed precision predicates to improve performance. For efficiency, we implement all geometry predicates using filtering techniques proposed by Shewchuk \cite{shewchuk1997adaptive}.

\subsection{Conversion}

\label{sec:convert}

We use Campen et al.'s method \cite{campen2010exact} for exact conversion of triangles from their vertex-based representation to plane-based representation. Given that the input vertex coordinate has $L$-bit precision including sign, the precisions of the four plane coefficients are $L_a, L_b, L_c, L_d$, which have to satisfy the following requirements:
\begin{equation}
\begin{split}
&L_a=L_b=L_c\ge 2(K-1)+1+1,\\
&L_d\ge(L_a-1)+(L-1)+2+1.
\end{split}
\end{equation}
Here $K$ is the maximum bits required to represent edge vector components in input meshes. If we use $M$ bits to store each plane coefficient, basically $M$ has to be greater than $L_d$. In our implementation, we actually use a more strong constraint $M \ge L_d+1$. Under this constraint, given a $L$-bit vertex $\bm{v_i}$, we can compute the orientation of plane $p_j$ with respect to $\bm{v_i}$ by the sign $\bm{n}(\bm{p_j})\cdot\bm{v_i} + d(\bm{p_j})$, which requires no more than $M$ bits. It allows very fast plane orientation predicates which accelerates the early rejection in our triangle-triangle intersection tests (\S \ref{section:isect}).

Let $\delta = 2^{K-L-1}$ be the relative length (in max-norm) of the longest edge in the mesh (relative to the bounding box). If we use IEEE 754 double float point number ($M=53$) and assume $\delta \le 2^{-5.5} \approx 0.022$, the maximum input precision $L$ can reach to 20, which is enough for most application (for standard IEEE 754 single float point number, the precision is 24-bit).

\subsection{Substrates}
\label{sec:substrates}
Plane-based geometry predicates used in our method include checking coincidence and co-orientation of planes, orientation of a plane with respect to a point, and whether three planes intersect in a unique point, etc. Most of them are well-discussed in previous work \cite{bernstein2009fast,banerjee1996topologically}. In the following, we focus on two advanced plane-based predicates, which are also important building blocks of our method.

@@

Since all the three vectors on the right side are already explicitly represented, we only have to evaluate the sign of an 3x3 matrix and avoid complicated high precision float-point arithmetic.
\begin{figure}
  \centering
  % Requires \usepackage{graphicx}
  \includegraphics[width=2.5in]{twopointoneline}\\
  \caption{The configuration of linear ordering of points. Points $\bm{v}_a$ and $\bm{v}_b$ are both on line $\bm{l}_{ab}$. We convert this problem into the plane ordering between $\bm{p}_a$ and $\bm{p}_b$ along $\bm{l}_{ab}$.}\label{fig:twopointoneline}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=2.5in]{circularorder}
\caption{The configuration of circular ordering of lines. $\bm{l}_a\colon(\bm{p}_0 \cap \bm{p}_a)$ and $\bm{l}_b\colon(\bm{p}_0 \cap \bm{p}_b)$ are coplanar in $\bm{p}_0$.}
\label{fig:circularorder}
\end{figure}

@@

\label{sec:embed}
According to the method described in \S\ref{sec:convert}, triangle faces $t$ are firstly converted to its P-rep: a supporting plane $\bm{p}_{t, sp}$ surrounded by three bounding planes $\{\bm{p}_{t, b}^i|\ i = 0,1,2\}$. We integrate the plane-based geometry into each of the tree steps of M\"{o}ller's algorithm as following:

@@

\begin{itemize}[leftmargin=0.45cm]
  \item[1)] The basic subroutine of the first step is given two faces $t_1$ and $t_2$, computing the orientation of of a face with respect to vertices from the other face. Reviewing the discussion of \S \ref{sec:convert}, under the constraint of $M \ge P+1$, we can compute the predicate within the precision of $M$ bits. This allow us to perform this early rejection efficiently.
      \vspace{0.5em}
  \item[2)] If $t_1$ and $t_2$ are not coplanar, the end points of $Seg_1$ and $Seg_2$ can be implicitly represented by plane triples. Take $Seg_1$ as an example. $Seg_1$ is the intersection between $t_1$ and $\bm{p}_{t_2, sp}$ and the end points of $Seg_1$ are intersections between $\bm{p}_{t_2, sp}$ and edges from $t_1$ (denoted as $\bm{e}^i_{t_1}$). Because $\bm{e}^i_{t_1}$ can be represented as $\bm{p}_{t_1, s}\cap \bm{p}^i_{t_1, b}$, the end points of $Seg_1$ can be represented in the form of $\bm{p}_{t_2, sp} \cap \bm{p}_{t_1, sp} \cap \bm{p}^i_{t_1, b}$. In Fig. \ref{fig:isect}, we list all possible intersecting situations between $t_1$ and $\bm{p}_{t_2, sp}$. The two intersection edges $\bm{e}^i_{t_1}$ for each situation are also presented. The coplanar situation will be discussed later in \S \ref{sec:degenerate}.
      \vspace{0.5em}
 \item[3)] The intersection between $t_1$ and $t_2$ is the overlap area of $Seg_1$ and $Seg_2$. It can be easily computed by sorting the end points of $Seg_1$ and $Seg_2$ along the line $\bm{l}\colon \bm{p}_{t_1, sp} \cap \bm{p}_{t_2, sp}$. Because end points are all represented using plane triples, we can use the linear order of points discussed in \S \ref{sec:substrates} to sort.
\end{itemize}

@@

%The criterion of whether an intersection help tessellation is by its necessity: if the intersection is not presented, whether some faces from the linked halfedge will cross the boundary of primitives. The word 'cross' do not only include the situation that a face is partly outside and partly inside of a primitive, but also can mean that a face is partly inside (outside) and part on the boundary of the primitive.
\begin{figure}[t]
\centering
\includegraphics[width=3.5in]{isolated}
\caption{Two situations of point intersections. (a) $\bm{v}_{iso}$ is isolated, and there is no adjacent intersection line segment. We need to add the $\bm{v}_{iso}$ to triangle $t_1$. (b) $\bm{v}_{non-iso}$ is not isolated. We do not need to add $\bm{v}_{non-iso}$ into $t_1$ because it can be added by other triangle pairs which intersect on line segments. However, for simplicity, we add the intersection point into $t_1$ in both situations.}
\label{fig:isolated}
\end{figure}

\subsubsection{Point intersection}
\label{sec:ipoint}
If two triangles intersect on a single point (Fig. \ref{fig:isolated}), the intersection cannot be represented using our four-component description. Therefore, we simply add the intersection point into the related triangles to guarantee correct tessellation, and no intersection is introduced.

@@

When intersection line segment lies on an edge (Fig. \ref{fig:twin}). we call it \emph{edge intersection}. The only difference between edge intersection and the general case is the neighborhood representation $\Psi$. The space near edge intersection is decided by both face in the two side of the intersected edge, instead of just one triangle face (Fig. X). Therefore, supposing intersection is on the edge $\bm{e}_{k, i}$ of mesh $P_k$, then the neighborhood $\Psi_k = \bm{e}_{k, i}$. Note that an intersection can be on edges from different meshes. Then there are more than one component of $\bm{\Psi}$ are edges (Fig. \ref{fig:twin}d).

@@

The key observation is that intersection in 2D does not create new valid edges. The word `valid` means the edge is necessary or possibly necessary for the final result mesh. We find that each intersection line segment in 2D is on the edges from input meshes. That means we can view 2D intersection as a special case of edge intersection. The only difference is that there can be up to three edge intersections in one 2D intersection (Fig. \ref{fig:coplanar}). As we have discussed, edge intersection will be detected twice. That means we can rely on the companion triangle faces to detect intersections. However, if the companion triangles are also coplanar, neither of the two triangles will record the intersection. In fact, we do not need to worry about this, because in this case, the intersection is not valid. The two sides of the intersection are both retained or both dropped and we do not need it for tessellation.

@@

@@

\section{Discussion}

\vspace{0.5em}

\subsection{Essential Subroutines}
\label{sec:esubroutine}

@@

@@

\vspace{0.5em}
\noindent\textbf{Classification acceleration}~~~~If the CSG tree is large with hundreds of primitive nodes, computing $\lambda_f(\bm{s}_i)$ from $\boldsymbol{\Lambda}(\bm{s}_i)$ for every face $\bm{s}_i$ can be costly. Thanks to the indicator space coherence, we can save the computation time by caching the evaluation result $f(\boldsymbol{\Lambda}(\bm{s}_i))$ during flood-filling.

\vspace{0.5em}
\noindent\textbf{Extend to piece-wise wind number mesh}~~~~Recent works claim that the piece-wise wind number (PWN) are more powerful to identify the inside and outside of meshes \cite{zhou2016mesh}. Our method is straightforward to apply PWN because we can use the neighborhoods of intersections to compute the PWN of each point easily. By using PWN, we can extend our input from regular set mesh without self-intersection to so-called PWN mesh that allows deficiencies such as self-intersection and multi-component. However, the cost of this extension is that we have to check every triangle pairs for intersections, even if they are from the same input mesh. Considering this cost, we prefer a pre-computation to resolve topology deficiencies only on those input meshes that we think that might be 'unclean'.

>>>>

We use Campen et al.'s method \cite{campen2010exact} for exact conversion of triangles from their vertex-based representation to plane-based representation. During the conversion, the coordinates of input vertices is rounded to certain precision which is dependent on the precision used to represent plane coefficients during boolean operation. If IEEE 754 double precision float-point number is used, 20-bit precision is allowed, which is enough for most CAD applications. As the precision of input coordinates is finite, we can determine in advance the upper boundary of precision needed to perform a precise decision, with which we can use fixed precision predicates to improve performance. For efficiency, we implement all geometry predicates using filtering techniques proposed by Shewchuk \cite{shewchuk1997adaptive}.

\iffalse
Given that the input vertex coordinate has $L$-bit precision including sign, the precisions of the four plane coefficients are $L_a, L_b, L_c, L_d$, which have to satisfy the following requirements:
\begin{equation}
\begin{split}
&L_a=L_b=L_c\ge 2(K-1)+1+1,\\
&L_d\ge(L_a-1)+(L-1)+2+1.
\end{split}
\end{equation}
Here $K$ is the maximum bits required to represent edge vector components in input meshes. If we use $M$ bits to store each plane coefficient, basically $M$ has to be greater than $L_d$. In our implementation, we actually use a more strong constraint $M \ge L_d+1$. Under this constraint, given a $L$-bit vertex $\bm{v_i}$, we can compute the orientation of plane $p_j$ with respect to $\bm{v_i}$ by the sign $\bm{n}(\bm{p_j})\cdot\bm{v_i} + d(\bm{p_j})$, which requires no more than $M$ bits. It allows very fast plane orientation predicates which accelerates the early rejection in our triangle-triangle intersection tests (\S \ref{section:isect}).

Let $\delta = 2^{K-L-1}$ be the relative length (in max-norm) of the longest edge in the mesh (relative to the bounding box). If we use IEEE 754 double float point number ($M=53$) and assume $\delta \le 2^{-5.5} \approx 0.022$, the maximum input precision $L$ can reach to 20, which is enough for most application (for standard IEEE 754 single float point number, the precision is 24-bit).
\fi

\label{sec:substrates}
Plane-based geometry predicates used in our method include checking coincidence and co-orientation of planes, orientation of a plane with respect to a point, and whether three planes intersect in a unique point, etc. Most of them are well-discussed in previous work \cite{bernstein2009fast,banerjee1996topologically}. In the following, we focus on two advanced predicates, which are also important building blocks of our method.

@@

Since all the three vectors on the right side are already explicitly represented, we only have to evaluate the sign of an 3$\times$3 matrix and avoid complicated high precision float-point arithmetic.
\begin{figure}
  \centering
  % Requires \usepackage{graphicx}
  \includegraphics[width=3.5in]{twopointoneline}\\
  \caption{The configuration of linear ordering of points. Points $\bm{v}_a$ and $\bm{v}_b$ are both on line $\bm{l}_{ab}$. We convert this problem into the plane ordering of $\bm{p}_a$ and $\bm{p}_b$ along $\bm{l}_{ab}$.}\label{fig:twopointoneline}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=3.5in]{circularorder}
\caption{The configuration of circular ordering of lines. $\bm{l}_a\colon(\bm{p}_0 \cap \bm{p}_a)$ and $\bm{l}_b\colon(\bm{p}_0 \cap \bm{p}_b)$ are coplanar in $\bm{p}_0$.}
\label{fig:circularorder}
\end{figure}

@@

\label{sec:embed}
Given a triangle face $t$, it is firstly converted to its P-rep: a supporting plane $\bm{p}_{t, sp}$ surrounded by three bounding planes $\{\bm{p}_{t, b}^i|\ i = 0,1,2\}$. We integrate the plane-based geometry into each of the tree steps of M\"{o}ller's algorithm as following:

@@

\begin{itemize}[leftmargin=0.45cm]
  \item[1)] The basic subroutine of the first step is given two faces $t_1$ and $t_2$, computing the orientation of of a face with respect to vertices from the other face. We find that since the exact coordinates of each triangle corners are known, we can compute the point-plane orientation within the precision of plane coefficients---namely, using simple fix float-point arithmetic. This allow us to perform this early rejection efficiently.
      \vspace{0.5em}
  \item[2)] If $t_1$ and $t_2$ are not coplanar, the end points of $Seg_1$ and $Seg_2$ can be implicitly represented by plane triples. Take $Seg_1$ as an example. $Seg_1$ is the intersection between $t_1$ and $\bm{p}_{t_2, sp}$ and the end points of $Seg_1$ are intersections between $\bm{p}_{t_2, sp}$ and edges from $t_1$ (denoted as $\bm{e}^i_{t_1}$). Because $\bm{e}^i_{t_1}$ can be represented as $\bm{p}_{t_1, s}\cap \bm{p}^i_{t_1, b}$, the end points of $Seg_1$ can be represented in the form of $\bm{p}_{t_2, sp} \cap \bm{p}_{t_1, sp} \cap \bm{p}^i_{t_1, b}$. In Fig. \ref{fig:isect}, we list all possible intersecting situations between $t_1$ and $\bm{p}_{t_2, sp}$. The two intersection edges $\bm{e}^i_{t_1}$ for each situation are also presented. The coplanar situation will be discussed later in \S \ref{sec:degenerate}.
      \vspace{0.5em}
 \item[3)] The intersection between $t_1$ and $t_2$ is the overlap area of $Seg_1$ and $Seg_2$. It can be easily computed by sorting the end points of $Seg_1$ and $Seg_2$ along the line $\bm{l}\colon \bm{p}_{t_1, sp} \cap \bm{p}_{t_2, sp}$. Because end points are all represented using plane triples, we can use the linear order of points discussed in \S \ref{sec:substrates} to sort.
\end{itemize}

@@

%The criterion of whether an intersection help tessellation is by its necessity: if the intersection is not presented, whether some faces from the linked halfedge will cross the boundary of primitives. The word 'cross' do not only include the situation that a face is partly outside and partly inside of a primitive, but also can mean that a face is partly inside (outside) and part on the boundary of the primitive.

\iffalse
\begin{figure}[t]
\centering
\includegraphics[width=3.5in]{isolated}
%\caption{Two situations of point intersections. (a) $\bm{v}_{iso}$ is isolated, and there is no adjacent intersection line segment. We need to add the $\bm{v}_{iso}$ to triangle $t_1$. (b) $\bm{v}_{non-iso}$ is not isolated. We do not need to add $\bm{v}_{non-iso}$ into $t_1$ because it can be added by other triangle pairs which intersect on line segments. However, for simplicity, we add the intersection point into $t_1$ in both situations.}
\label{fig:isolated}
\end{figure}
\fi

\subsubsection{Point intersection}
\label{sec:ipoint}
If two triangles intersect on a single point (e.g., Fig. \ref{fig:isect}d), the intersection cannot be represented using our four-component description since the line segment collapses into a single point. In these cases, we simply add the intersection point into the related triangles to guarantee correct tessellation, and no intersection is introduced.

@@

When intersection line segment lies on an edge (Fig. \ref{fig:twin}). we call it \emph{edge intersection}. The speciality of edge intersection is the neighborhood representation $\Psi$. The space near edge intersection is divided by both face in the two side of the intersected edge, instead of just one triangle face (Fig. X). Therefore, supposing intersection is on the edge $\bm{e}_{k, i}$ of mesh $P_k$, we denote the neighborhood as $\Psi_k = \bm{e}_{k, i}$. Note that an intersection can be on edges from different meshes. Then there are more than one component of $\bm{\Psi}$ are edges (Fig. \ref{fig:twin}d).

@@

The key observation is that intersections in 2D are either duplicated added or invalid. The word `valid` means the intersections will appear as an edge in the final mesh. Namely, faces of intersection neighborhood have different classification results:
\begin{equation}
\lambda_f(\bm{s^i}) = f(\bm{\Lambda}(\bm{s}_i)) = constant, \bm{s}^i \in \mathcal{N}(\mathcal{I})
\end{equation}
, where $f$ is the CSG function, and $\bm{s}^i \in \mathcal{N}(\mathcal{I})$ is the neighboring faces of intersection $\mathcal{I}$. In principle, the validation of intersection is not known until classification stage. However, we can perform an early rejection to eliminate intersections that are invalid in certain.

We find that each intersection line segment in 2D is on the edges from input meshes. That means we can view 2D intersection as a special case of edge intersection. The only difference is that there can be up to three edge intersections in one 2D intersection (Fig. \ref{fig:coplanar}). As we have discussed, edge intersection will be detected twice. That means we can rely on the companion triangle faces to detect intersections. However, if the companion triangles are also coplanar, neither of the two triangles will record the intersection. Fortunately, in this case, the intersection is not valid. The two sides of the intersection have the same indicators and are both retained or both dropped and we do not need it for tessellation.

@@

\subsection{Acceleration by Caching}
\label{sec:acc}
If the CSG tree is large with hundreds of primitive nodes, computing $\lambda_f(\bm{s}_i)$ from $\boldsymbol{\Lambda}(\bm{s}_i)$ for every face $\bm{s}_i$ can be costly. Thanks to the indicator space coherence, we can save the computation time by caching the evaluation result $f(\boldsymbol{\Lambda}(\bm{s}_i))$ during flood-filling.

\subsection{Tessellating on Classification}
We find for a CSG with many meshes, a large percentage of intersections are invalid (see \S\ref{sec:degenerate} for 'invalid'). Tessellation according to these invalid intersections is not necessary. To avoid unnecessary tessellation, we can give an early prediction of which intersections are invalid by intersections information of faces, but have to embed the tessellation stage into the classification stage, which we call it 'tessellating on classification'.

In most situations, a certain faces $\bm{s}$ only intersect with a few other meshes $\Theta(\bm{s})$. We can use the same cache strategy in \S\ref{sec:acc} to shrink the original CSG into a smaller one by the common indicators of $\{P_i\}\backslash\Theta(\bm{s})$, where $\{P_i\}$ means all the primitive meshes. After the shrinking, the primitive meshes of the CSG must be from $\Theta(\bm{s})$. If any mesh in $\Theta(\bm{s})$ does not appear in the shrinked CSG, it means the indicator of that mesh does not change the classification result, which in another word, intersections on $\bm{s}$ from that mesh are invalid and do not affect the classification of any subfaces of $\bm{s}$. If the shrinked CSG is trivial which does not contain any primitives, it means $\bm{s}$ does not need tessellation. In this way, we save the computation time, and simplify the topology of the final result mesh. Because we can only shrink the CSG for $\bm{s}$ when we classify it---before that the indicators of meshes from $\{P_i\}\backslash\Theta(\bm{s})$ are not known---we do not perform tessellation until we do the classification.

@@

\section{Essential Subroutines}
\label{sec:esubroutine}

@@

\begin{table*}[ht]
\caption{Computation Time Statistics of Binary Boolean Operation (Seconds)}
\label{tab:performance}
\centering
\begin{tabular}{*{9}{c|}c}%*{4}{>{\centering\arraybackslash}p{35pt}}}
\hline
{No.} & {Figure} & {Triangle Num. 1} & {Triangle Num. 2} &
CGAL & Maya & Cork & Carve & QuickCSG & Our Method
\\
\hline\hline
1 & budda \& lion & 1.08M & 0.4M & - & - & - & - & 3.44 & 6.88\\
2 & dragon \& bunny & 277k & 70k & - & - & - & - & - & -\\
3 & armadillo \& armadillo* & 150k & 150k & - & - & - & - & - & -\\
4 & horse \& corpse & 150k & 150k & - & - & - & - & - & -\\
5 & dinasour \& ironman & 150k & 150k & - & - & - & - & - & -\\
\hline
\end{tabular}
\begin{flushleft}

\end{flushleft}
\end{table*}

\begin{table*}[ht]
\caption{Computation Time Statistics of Large CSG Evaluation (Seconds)}
\label{tab:performance}
\centering
\begin{tabular}{*{9}{c|}c}%*{4}{>{\centering\arraybackslash}p{35pt}}}
\hline
{No.} & {Figure} & {Triangle Num.} & {Primitive Num.} &
CGAL* & Maya* & Cork & Carve & QuickCSG & Our Method
\\
\hline\hline
1 & Sprocket & 1.08M & 0.4M & - & - & - & - & 3.44 & 6.88\\
2 & ring and ball & 277k & 70k & - & - & - & - & - & -\\
3 & t1 & 150k & 150k & - & - & - & - & - & -\\
4 & t2 & 150k & 150k & - & - & - & - & - & -\\
5 & h & 150k & 150k & - & - & - & - & - & -\\
6 & Organic & 150k & 150k & - & - & - & - & - & -\\
7 & 6 Budda & 150k & 150k & - & - & - & - & - & -\\
8 & Serpent & 150k & 150k & - & - & - & - & - & -\\
9 & Dithering & 150k & 150k & - & - & - & - & - & -\\
\hline
\end{tabular}
\begin{flushleft}
$^{\nabla}$~~\emph{Min} (\emph{Max}) means the minimum (maximum) number of faces of a single primitive.

$^{\circ}$~~The total computation time of our method includes the construction of half-edge structure and the three steps in Section \ref{sec:overview}.

\end{flushleft}
\end{table*}

We implemented the proposed method in C++ and tested a series of models on a laptop with Intel Core i5 1.5GHz CPU and 8GB RAM. To prove both the efficiency and robustness, we perform boolean evaluation on various CSGs with different complexity. Extreme degenerate cases such as self-union are also tested.

We compared our method with several previous works with available implementations, including CGAL \cite{cgal:hk-bonp3-15a}, Maya \cite{Maya2015,barki2015exact},"Cork" \cite{Cork}, "QuickCSG" \cite{douze2015quickcsg}, "Carve" \cite{Carve}, and online service of Campen and Kobbelt's plane-based method \cite{campen2010exact,WebBSP}.

\vspace{0.5em}
\noindent\textbf{Coplanar and self-union}~~~~
Our method is unconditionally robust for regular set meshes. Even extreme degenerate cases will not cause invalid output. To prove that, we tested the self-union of several models and some CSG with coplanar faces. We find that our method always produces visually correct results. QuickCSG and Cork failed to produce the result in most of these cases, because they cannot deal with coplanar faces. Even after perturbation, their results are still full with deficiencies (holes, boundary edges, etc.). For the bunny model, we found our result face count was slightly deviated from the original mesh. This is because the original mesh contains self-intersection in the bunny chest (the green faces), which causes errors during classification.

\vspace{0.5em}
\noindent\textbf{Binary boolean operations}~~~~
The most common situation of CSG evaluation is to perform boolean operations one by one, since many designers are used to modify models progressively. While our method can evaluate multiple boolean operations once for all, we also compared the performance of binary boolean operations to prove the efficiency. Table \ref{tab:performance} shows the evaluation time of different methods. We can clearly see our method is very fast that is only slightly slower than the fastest non-robust QuickCSG. Other robust methods such as Maya and CGAL are much slower because both of them use the arbitrary precision arithmetic. It should be noted that in some cases (), most time is spent on octree construction in our method. It means other stages which involve plane-based geometry take only a small percentage of time, proving the efficiency of our plane-based geometry.

\vspace{0.5em}
\noindent\textbf{CSGs with large number of meshes}~~~~
To identify the ability of evaluating large CSG, we also test some CSG with tens or hundreds of meshes. Maya and CGAL cannot perform multiple boolean operations, so we can only give the comparison of incremental boolean evaluation for these methods. We see that the computation time of robust methods like CGAL and Maya grows rapidly when the number of meshes grows. On the other hand, our method keeps good performance while stay robust. During our experiments, we noticed Maya gives the correct results in the first few boolean operations, but failed in the later ones. It proves another disadvantage of incremental boolean operation methods: if it cannot guarantee exactness, it will accumulate numerical errors which affects the algorithm stability.

@@

\vspace{0.5em}
\noindent\textbf{Extend to piece-wise wind number meshes}~~~~Recent works claim that the piece-wise wind number (PWN) are more powerful to identify the inside and outside of meshes \cite{zhou2016mesh}. Our method is straightforward to apply PWN because we can use the neighborhoods of intersections to compute the PWN of each point easily. By using PWN, we can extend our input from regular set mesh without self-intersection to so-called PWN mesh that allows deficiencies such as self-intersection and multi-component. However, the cost of this extension is that we have to check every triangle pairs for intersections, even if they are from the same input mesh. Considering this cost, we prefer a pre-computation to resolve topology deficiencies only on those input meshes that we think that might be 'unclean'.
